\cvsection{Research}

\begin{cventries}
  \cventry
    {\vspace{-20pt}} %
    {International Journal Publications \& International Conference Publications} % Title
    { } % Location
    { } % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Landmark transfer with minimal graph, V. Mykhalchuk, F. Cordier, H. Seo, Computers \& Graphics Journal.}
        \item {On spatio-temporal feature point detection for animated meshes, V. Mykhalchuk, H. Seo, F. Cordier, The Visual Computer Journal.}
        \item {AniM-DoG: A Spatio-Temporal Feature Point Detector for Animated Mesh, Vasyl Mykhalchuk, Computer Graphics International 2014, Sydney, Australia.}
        \item {Correspondance de maillages dynamiques basée sur les caractéristiques (Doctoral Thesis), English title: Feature-based matching of animated meshes.}
      \end{cvitems}
    }
   
   \cventry
   {}
   {Sub-reviewer}
   {}
   {}
   {
     \begin{cvitems}
     \item{Computer Analysis of Images and Patterns (CAIP), 2013.}
     \item{Computer Animation and Social Agents (CASA), 2013.}
	 \item{Computer Graphics International (CGI), 2013.}
     \end{cvitems}
   } % Description
   
   \cventry
   {}
   {Other communications}
   {}
   {}
   {
     \begin{cvitems}
     \item Surface registration: static and dynamic cases, V. Mykhalchuk, Presentation in the mid-term  follow-up of the PhD thesis, Strasbourg, 2013. 
\item Landmark Transfer with Minimal Graph, V. Mykhalchuk, Poster, Journée Poster École Doctorale  "MSII", Université de Strasbourg, 2012. 
\item Landmark Transfer with Minimal Graph, V. Mykhalchuk, internal talk at IGG team, Université  de Strasbourg, 2012. 
     \end{cvitems}
   }
   
   \cventry
   {\href{http://www.miralab.ch/}{MIRALab Research Group}}
   {Visiting Researcher}
   {\textbf{University of Geneva, Switzerland}}
   {Summer 2013}
   { } % Description
   
   \cventry
   {}
   {Co-supervision}
   {}
   {}
   {
     \begin{cvitems}
     \item{Guillaume Peiffert (summer internship, 2014)}
     \item{Ming Zhang (internship E1, 2013)}
	 \item{Christophe Klein  (Master M2S3 project, 2013)}
     \end{cvitems}
   } % Description

\end{cventries}
